\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-27 tex/ms.tex
blurb

Residuals in Figure~\ref{fig:model} display significant correlated
structure. Talk about their power spectrum. Talk about how S2 is worse fit.

@@

\todo{For realz, how would we do this.}

>>>>

\todo{Residuals in Figure~\ref{fig:model} display significant correlated
structure. Talk about their power spectrum. Temporal fit helps. Discuss
Figure~\ref{fig:map_temporal} and argue we have evidence for clouds.}

@@

\todo{Discuss how we would we do this for an actual exoplanet, and
all the homework we need to do before that happens.}
